Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Improved wording of sentence in section 2.1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1146 ccdd05d5-56c1-461a-bf98-85f6876523b4

Optical flashes have only been observed for a handful of long
\GRB{}s \citep{2011CRPhy..12..255A} by telescopes with extremely rapid response
or, in the case of \textsc{grb 080319b}, by pure serendipity, where several
telescopes were observing a previous \GRB{} in the same
field \citep{2008Natur.455..183R}. The observed optical flashes peaked
within tens of seconds and decayed quickly.
Short \GRB{}s, on the other hand, typically
fade too quickly to even catch the tails of the afterglows in any band. Rapid
\GW{} transient alerts could enable the first observation of
prompt optical flashes and the rise of afterglows from short \GRB{}s, and, for
a truly exceptional event, perhaps even a glimpse of a
precursor \citep{0004-637X-723-2-1711}.

>>>>

Optical flashes have only been observed for a handful of long
\GRB{}s \citep{2011CRPhy..12..255A} by telescopes with extremely rapid response
or, in the case of \textsc{grb 080319b}, by pure serendipity, where several
telescopes were already observing the afterglow of another \GRB{} in the same
field of view~\citep{2008Natur.455..183R}. The observed optical flashes peaked
within tens of seconds and decayed quickly.
Short \GRB{}s, on the other hand, typically
fade too quickly to even catch the tails of the afterglows in any band. Rapid
\GW{} transient alerts could enable the first observation of
prompt optical flashes and the rise of afterglows from short \GRB{}s, and, for
a truly exceptional event, perhaps even a glimpse of a
precursor \citep{0004-637X-723-2-1711}.
